%-------------------------
% Cover Letter in Latex
% Author : Vinayaka Sajjanshetty
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\pdfgentounicode=1

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Vinayaka Sajjanshetty} \\ \vspace{4pt}
    \small
    \faPhone \thinspace +81-7084689061 \quad
    \faEnvelope \thinspace \href{mailto:hellovinayakasajjanshetty@gmail.com}{hellovinayakasajjanshetty@gmail.com} \quad
    \faMapMarker \thinspace Hamamatsu, Japan \\ \vspace{3pt}
    \faLinkedin \thinspace \href{https://www.linkedin.com/in/vinayaka-sajjanshetty-91033111a}{linkedin.com/in/vinayaka-sajjanshetty} \quad
    \faGithub \thinspace \href{https://github.com/vinayakas1997}{github.com/vinayakas1997} \quad
    \faGlobe \thinspace \href{https://vinayakas1997.github.io/my-project-docs/}{vinayakas1997.github.io}
\end{center}

\vspace{10pt}

\textbf{To the OpenAI Hiring Team,}

\vspace{6pt}

I am writing to express my strong interest in the \textbf{Forward Deployed Engineer (FDE)} role at OpenAI.

Unlike traditional software engineering where ownership ends at a PR merge, an FDE owns the complete lifecycle of customer success---embedding directly into enterprise environments, navigating legacy constraints, and shipping production-grade solutions on day one. My experience operating at the intersection of agentic AI, enterprise deployments, and cross-border technical leadership maps directly to this philosophy.

\vspace{6pt}

\textbf{Enterprise Deployment Under Strict Constraints:} At Somic Ishikawa, I built and deployed fully on-premise RAG pipelines under a strict ``No External API'' data governance policy---ingesting 2,500+ bilingual documents, solving layout-aware OCR failures (reducing error rates from 45\% to near zero), and delivering 360$\times$ query speedup for a 10-member planning team. The same platform was later adopted by the \textbf{PLC Code Design team}, extending it to 500-page technical manuals with entity-anchored metadata enrichment achieving \textbf{85-90\% retrieval accuracy} on register-level queries.

\vspace{6pt}

\textbf{Production Agentic AI Systems:} I designed and shipped EDAS, an event-driven multi-agent framework (LangGraph) deployed on live factory PostgreSQL databases---featuring Manager/Planner/Executor agents, AST-based SQL security guardrails, and pessimistic concurrency control (\texttt{SELECT...FOR UPDATE SKIP LOCKED}). This is the closest analogue to what FDEs ship: agentic AI in production, integrated with real customer infrastructure.

\vspace{6pt}

\textbf{End-to-End Performance Ownership:} When deployment required on-premise inference optimization, I refactored the serving stack---doubling throughput (35$\to$80 tok/s), cutting latency (90s$\to$6-10s), and building a Human-in-the-Loop evaluation dashboard for client domain experts to self-serve regression testing. I also served as the primary technical bridge between US engineering partners and Japan factory teams, translating field friction into product improvements.

\vspace{6pt}

I bring full-stack fluency (Python, TypeScript, React, LangGraph), deep agentic systems experience, and the field-tested empathy required to earn customer trust and unblock complex technical roadblocks. I would welcome the opportunity to discuss how my deployment background can support OpenAI's enterprise goals.

\vspace{20pt}

Sincerely,

\vspace{14pt}

\textbf{Vinayaka Sajjanshetty}

\end{document}
